Topic 21: AUG experiment Week 17 Summary

### 2017-04-28 Meetings/AUGrelated/summaryWeek17_280417.tex
Slides for summary of 28 of April

\documentclass[10pt, compress]{beamer}
\usetheme[conference=KoM,venue=Remote, date=03/13/2017, titleprogressbar, logo=RFX-logo]{Eurof}
\usepackage{listings,amsmath,multimedia, amssymb}
\usepackage{../beamerclass/tangocolors}
\usepackage{../beamerclass/rfxcolor}
% for drawing
\usepackage{pgf}
\usepackage{tikz}
\usetikzlibrary{arrows,shapes,backgrounds}
\usepackage{../beamerclass/onimage}
\usepackage[export]{adjustbox}
\usepackage{bm}
% for font
\usepackage[absolute,overlay]{textpos}
  \setlength{\TPHorizModule}{1mm}
  \setlength{\TPVertModule}{1mm}

\usepackage[style=nature,citestyle=authoryear-comp,defernumbers=true,maxnames=2,firstinits=true,
uniquename=init,backend=bibtex8,arxiv=abs,mcite]{biblatex}
\bibliography{biblio}
\renewcommand*{\bibfont}{\footnotesize}
\renewcommand*{\citesetup}{\footnotesize}
\usepackage[export]{adjustbox}
\makeatother
\mode<presentation>
\makeatletter
% add a macro that saves its argument
\newcommand{\footlineextra}[1]{\gdef\insertfootlineextra{#1}}
\newbox\footlineextrabox
% for reducing font on a single slide
\newcommand\Fontvi{\fontsize{8}{7.2}\selectfont}
\title{Topic 21: AUG experiment}
\date{24 April 2017}
\author[Topic 21 Scientific Team]{Topic 21 Scientific Team}
\begin{document}
\tikzstyle{every picture}+=[remember picture]
\maketitle

@@

@@

\begin{frame}{Required diagnostic and analysis}
  \begin{itemize}
    \item[$\boxtimes$] Midplane Manipulator
    \item[$\boxtimes$] Li-Beam profiles (inter-ELMs one in the H-Mode
      shots) and fluctuations
    \item[$\boxtimes$] RFA \#2
    \item[$\boxtimes$] Divertor probes. Evaluation inter-shot of
      profiles and rollover density. Divertor collisionality
    \item[$\boxtimes$] Neutral profiles
    \item[$\square$] Infrared for probe head monitoring
    \item[$\boxtimes$] Reflectometer including the multi-channel one
      for the operation at 1.9 T
    \item[$\square$] Bolometer/AXUV in the divertor region. We need
      the monitoring of radiation front movement. Can we get inverted
      and tomography inter shot?
    \item[$\square$] Gauges and neutral measurement
    \item[$\boxtimes$] SXR
    \item[$\boxtimes$] FILD  
    \end{itemize}
\end{frame}

\begin{frame}{HFF probe head}
  \begin{columns}
    \begin{column}{0.5\textwidth}
      \includegraphics[width=.9\textwidth, angle=-10]{pdfbox/HeadConfiguration}
    \end{column}
    \begin{column}{0.5\textwidth}
      \begin{itemize}
      \item \textcolor{red}{Ion saturation current}
      \item \textcolor{blue}{Floating potential}
        \item \textcolor{green}{Swept probe for T$_e$ and $n_e$}
        \item Intershot analysis for blob-size, autocorrelation
      \end{itemize}
    \end{column}
  \end{columns}

\end{frame}
\end{document}

>>>>

\documentclass[10pt, compress]{beamer}
\usetheme[conference=KoM,venue=Remote, date=28/04/2017, titleprogressbar, logo=RFX-logo]{Eurof}
\usepackage{listings,amsmath,multimedia, amssymb}
\usepackage{../beamerclass/tangocolors}
\usepackage{../beamerclass/rfxcolor}
% for drawing
\usepackage{pgf}
\usepackage{tikz}
\usetikzlibrary{arrows,shapes,backgrounds}
\usepackage{../beamerclass/onimage}
\usepackage[export]{adjustbox}
\usepackage{bm}
% for font
\usepackage[absolute,overlay]{textpos}
  \setlength{\TPHorizModule}{1mm}
  \setlength{\TPVertModule}{1mm}

\usepackage[style=nature,citestyle=authoryear-comp,defernumbers=true,maxnames=2,firstinits=true,
uniquename=init,backend=bibtex8,arxiv=abs,mcite]{biblatex}
\bibliography{biblio}
\renewcommand*{\bibfont}{\footnotesize}
\renewcommand*{\citesetup}{\footnotesize}
\usepackage[export]{adjustbox}
\makeatother
\mode<presentation>
\makeatletter
% add a macro that saves its argument
\newcommand{\footlineextra}[1]{\gdef\insertfootlineextra{#1}}
\newbox\footlineextrabox
% for reducing font on a single slide
\newcommand\Fontvi{\fontsize{8}{7.2}\selectfont}
\title{Topic 21: AUG experiment Week 17 Summary}
\date{28 April 2017}
\author[Topic 21 Scientific Team]{Topic 21 Scientific Team}
\begin{document}
\tikzstyle{every picture}+=[remember picture]
\maketitle

@@

\begin{frame}{Current scan at constant q$_95$}
  \Fontvi
  \begin{columns}
    \begin{column}{0.6\textwidth}
      \includegraphics[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/IpConstantq95_density}
    \end{column}
    \begin{column}{0.4\textwidth}
      \begin{itemize}
        \item Succesfull plasma current scan at constant
          q$_{95}$ (\# 34102,  34103, 34104).
        \item Actually at higher current $\overline{n}_e$ too
          high?
        \item It is true the flattening occurs earlier in density at
          lower current?
      \end{itemize}
    \end{column}
  \end{columns}

\end{frame}

\begin{frame}{Current scan at constant q$_95$}
  \Fontvi
  \begin{columns}
    \begin{column}{0.6\textwidth}
      \includegraphics[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/IpConstantBt_density}
    \end{column}
    \begin{column}{0.4\textwidth}
      \begin{itemize}
        \item At constant B$_t$ the flattening is less robust? Compare
          for example higher current at same density
      \end{itemize}
    \end{column}
  \end{columns}
\end{frame}

@@

\begin{frame}{H-Mode}
  \Fontvi
  \begin{columns}
    \begin{column}{0.6\textwidth}
      \includegraphics[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/DegradedHModeMarked}
    \end{column}
    \begin{column}{0.4\textwidth}
      \begin{itemize}
        \item 3 Shots obtained (1 not in our budget?) \# 34107
          (3.4MW), 34108 (5.4MW),
          34115(5.4MW)
        \item The last two shots encountered at the end a phase of
          degraded H-Mode.
        \item Reducing the N seeding in \# 34115 allows to skip part
          of the phases. Can we try to reduce further? \alert{Keep in
            mind we need to readjust all considering the lack of cryopumps}
      \end{itemize}
    \end{column}
  \end{columns}
\end{frame}

\begin{frame}{Analysis to be done: brainstorming}
  \begin{itemize}
    \item Blob size, velocity, collisionality scaling
      (D. Carralero). Proper calculaton of L$_{\parallel}$ (N. Vianello)
    \item Limiter probe analysis (S. Costea)
    \item Profile and$\lambda_n$ evolution also in inter-ELM phases Li-Beam
      (F. Laggner)
    \item Reflectometry. Profile evolution and Fluctuations (IST)
    \item Fast ions (K. McClements and J. Galdon-Quiroga)
    \item Divertor evolution and rollover time (W. Zhang)
    \item Radiation (M. Bernert and N.Vianello)
    \item Further statistical analysis (structure function, increments
      PDF scaling) (M.Spolaore)
    \item Others??
  \end{itemize}
\end{frame}
\end{document}
